---
title: "Reproducible Document"
author: "LKT/rostools"
format: html
---

```{r setup}
#| message: false
#| warning: false

library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
```

## About me

- Lisbeth Koch Thomsen
- MBH lab, SDU

**Love dogs** 
*time*

## Simple code

```{r}
3 * 3
```


## Writing R code

2 + 2

```{r}
2 + 2
```

## Testing for Git
All the best for confusion
noget nyt

## Showing the data

```{r}
post_meal_data

glimpse(post_meal_data)
```

## Plot one continuous variable

```{r}
#| fig-cap: "Write your figure caption here eg. Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

See @fig-bmi-histo

## Exercise: discrete plots

```{r}
#| fig-cap: "Cool figure caption about glykemi"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-group-bar above for a cool plot!



```{r}
#| fig-cap: "Cool figure caption about Group"
#| label: fig-groupgroup-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-groupgroup-bar above for a cool plot!

## Plotting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```


## Side by side plots

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap:
#|  - "distribution of BMI"
#|  - "number of those with glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous vaiables

```{r}
#| fig-cap: "Scatterplot of BMI and the area under the curve for glucose"
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```
